% LaTeX file for resume 
% This file uses the resume document class

\documentclass[]{res}
%\setlength\parindent{24pt}
% the margin option causes section titles to appear to the left of body text 
\textwidth=6in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\begin{document} 
\raggedleft Last updated \today
%\textbf{Curriculum Vitae}\\
%\textbf{Statistics PhD program}\\
%\textbf{U-M ID: 31735397}
\name{Cheng-Han Yu\\[10pt]}% the \\[12pt] adds a blank line after name 
\address{Jack Baskin School of Engineering \\ 1156 High Street \\ Santa Cruz, CA 95064 USA}
\address{Phone: 812-361-9976 \\ Email: \href{mailto:cheyu@soe.ucsc.edu}{cheyu@soe.ucsc.edu}\\Web: \url{http://chenghanyu.github.io}}
 
\begin{resume}
\raggedright
%\section{Personal}
% Nationality: Taiwan\\
% Date of Birth: August 26

\section{Education}
\textbf{University of California, Santa Cruz}, USA\\ 
- Ph.D. Candidate in Statistics and Applied Mathematics. Advisor: Prof. Raquel Prado

 
\textbf{Indiana University Bloomington}, USA\\
- Ph.D. program in Statistical Science, Aug 2011 - May 2013. Advisor: Prof. Gabriel Huerta\\
- M.A. in Economics, May 2012.
 %Ph.D minor: Mathematics\\
 %\textit{Dissetation:\\
 % M.A. in Economics, Indiana University Bloomington, USA, May 2012.
 
\textbf{National Chengchi University}, Taiwan\\
- M.A. in Public Finance, July 2005. Advisor: Prof. K.L. Glen Ueng\\
- B.A. in Public Finance, June 2003.

\section{Research\\Interests}
Bayesian spatio-temporal modeling with application in brain imaging, high-dimensional data analysis, variable selection, data visualization.
 
 \section{Publications}

\underline{Published papers:}
\begin{enumerate}
	\item Feldman, S.R., R. Balkrishnan, H. C. Lin, \textbf{C. H. Yu}, and S.A. Davis (2014). Underuse of Early Follow-Up Visits: A Missed Opportunity to Improve Patients' Adherence. \textit{Journal of Drugs in Dermatology}, 13(7):833-836.
	\item Ueng, K.L.G. and \textbf{C. H. Yu} (2008). The Neutrality of Profit Tax - Two-Phase Decision Model Under Uncertainty of Economy. \textit{Taiwan Public Finance Review}, 40, 4, 118-130.
	\item \textbf{Yu, C. H.} (2005). Master thesis: \textit{"The Output and Tax Evasion Decisions of Monopolistic Firm - Under the Conditions of Limited Liability and Market Uncertainty"}
\end{enumerate}
%\begin{itemize} %\itemsep -2pt
% \item[1.] Feldman, S.R., R. Balkrishnan, H. C. Lin, \textbf{C. H. Yu}, and S.A. Davis (2014). Underuse of Early Follow-Up Visits: A Missed Opportunity to Improve Patients' Adherence. \textit{Journal of Drugs in Dermatology}, 13(7):833-836.
% \item[2.] Ueng, K.L.G. and \textbf{C. H. Yu} (2008). The Neutrality of Profit Tax - Two-Phase Decision Model Under Uncertainty of Economy. \textit{Taiwan Public Finance Review}, 40, 4, 118-130.
% \item[3.] \textbf{Yu, C. H.} (2005). Master thesis: \textit{"The Output and Tax Evasion Decisions of Monopolistic Firm - Under the Conditions of Limited Liability and Market Uncertainty"}
% 
%\end{itemize}
%\underline{Work in process:}
%\begin{itemize} %\itemsep -2pt
% \item[1.] 
%\end{itemize}

\underline{Papers under review:}
\begin{enumerate}
	\item \textbf{Yu, C. H.}, R. Prado, H. Ombao, and D. Rowe (2016). A Bayesian Variable Selection Approach Yields Improved Brain Activation From Complex-Valued fMRI. 
%	Under Review, \textit{Journal of American Statistical Association, Application and Case Studies}. 
\end{enumerate}

\underline{Technical reports:}
\begin{itemize}
\item[1.] Liu, S. Z., \textbf{C. H. Yu}, F. H. Lin, W. L. Wang, C. L. Wu (2008). Research on Regional Characteristics, Industry Clusters and Competitiveness Assessment Index of Taiwan Districts, granted by National Science Council, Taiwan
\end{itemize}
\underline{Current research projects:}
\begin{itemize} %\itemsep -2pt
%\item[1.] \textit{Axially symmetric processes and intrinsic random functions on the sphere}, National Science Foundation with Dr. Chunfeng Huang
\item[1.] \textit{Bayesian spatial hierarchical modeling of complex-valued fMRI signals}, with Prof. Raquel Prado
\end{itemize}

\section{Conference Posters:}
\begin{enumerate}
	\item \textit{Bayesian modeling of complex-valued fMRI signals}, ISBA 2016 World Meeting, June 2016, Sardinia, Italy, International Society for Bayesian Analysis
	\item \textit{Bayesian modeling of complex-valued fMRI signals}, Data Science Afternoon, May 2015, UC Santa Cruz
\end{enumerate}

\section{Invited Talks:}
\begin{enumerate}
	\item \textit{Bayesian spatial modeling of complex-valued fMRI signals}, \href{http://www.networkofmind.net/index.html}{Network of Mind 2017} and \href{http://sydney.edu.au/data-science/}{Center of Translational Data Science}, University of Sydney, Australia 2017.
	
	
\end{enumerate}

\section{Course projects:}
\begin{enumerate}
	\item \textit{Proper Scoring Rules}, UCSC AMS221 Bayesian Decision Theory (Prof. Bruno Sanso)
	\item \textit{Complex-valued EM Variable Selection of fMRI Signals}, UCSC AMS268 Advanced Bayesian Computation (Prof. Rajarshi Guhaniyogi)
	\item \textit{Numerical Linear Algebra: LU Decomposition with Pivoting for
Solving Linear Systems using Fortran and Python}, UCSC AMS209 Scientific Computing (Prof. Dongwook Lee)
	\item \textit{Particle Learning for Mixture Models}, UCSC AMS241 Bayesian Nonparametrics (Prof. Abel Rodriguez)
	\item \textit{Bayesian Parameter Estimation of Stochastic Differential Equations}, UCSC AMS216 Stochastic Differential Equations (Dr. Tatiana, Xifara)
	\item \textit{Markov Random Fields and the Ising Model}, UCSC AMS263 Stochastic Processes (Prof. Athanasios Kottas)
	\item \textit{Linear regression for Boston Housing - model checking, crossvalidation, and variable selection}, UCSC AMS256 Linear Models (Prof. Abel Rodriguez)
	\item \textit{The Bayesian Hierarchical Linear Regresssion Model on the Temperature of the Surface of the Sea}, UCSC AMS207 Bayesian Modeling (Prof. Bruno Sanso)
	\item \textit{Multivariate Analysis of Automobile Rating Data - Dimension reduction and Classification}, UCSC AMS225 Multivariate Statistics (Prof. Juhee Lee)
	\item \textit{A Review of Sample-path Optimization}, IUB S710 Statistical Computing (Prof. Michael Trosset)
	\item \textit{Ordinary Kriging and Spline on the Unit Circle}, IUB S681 Spatial Statistics (Prof. Chunfeng Huang)
	\item \textit{A Review of Particle Filtering and Parameter Learning}, IUB S681 Bayesian Computation (Prof. Gabriel Huerta)
	\item \textit{Derivation and Applications of Black-Scholes Partial Differential Equation and Black-Scholes formulas}, IUB M442 Partial Differential Equations II (Prof. Norm Levenberg)
	\item \textit{Taiwan GDP Forecasting, an Appication of SARIMA models}, IUB S650 Time Series Analysis (Prof. Jerome Busemeyer)
\end{enumerate}


\section{Experience}
 {\bf Instructor}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 	\item University of California, Santa Cruz \hfill 
 	\begin{itemize} \itemsep -2pt 
 		\item AMS 7L Statistical Methods for the Biological, Environmental, and Health Sciences Laboratory (Fall 2016)
 	\end{itemize}
 \end{itemize}
   \vspace{-0.3cm} 
 {\bf Research Assistant} with Prof. Shuen-Zen Liu, Center for Competitiveness and Innovation, Department of Accounting, National Taiwan University, 2007 - 2008
 \begin{itemize} 
 \item analyzing financial and economic indices to examine the competitiveness of Taiwan companies
 \item reading literatures, compiling information to assist Prof. Liu in publishing his book about performance management\footnote{http://www.readingtimes.com.tw/timeshtml/ad/DH0185/index.html} 
 \end{itemize}
 {\bf Research Assistant} with Prof. Li-Chen Hsu, Department of Public Finance, National Chengchi University, 2005
 \begin{itemize}
 \item Experimental Study on the Effects of Reputation and Fairness on Cooperation in the Voluntary Contribution Mechanism, granted by the National Science Council, Taiwan
 \end{itemize}
 {\bf Teaching Assistant}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item University of California, Santa Cruz \hfill
  	\begin{itemize}\itemsep -2pt 
 	\item AMS7 Statistical Methods for the Biological, Environmental, and Health Sciences (Spring 2016, T. Xifara; Summer 2015, B. Mendes; Winter 2015, R. Prado)
 	\item AMS131 Introduction to Probability Theory (Summer 2016, D. Draper; Spring 2014, R. Morris)
 	\item AMS203 Introduction to Probability Theory (Fall 2015, R. Prado)
 	\end{itemize}
 \item Indiana University Bloomington \hfill
 	\begin{itemize}\itemsep -2pt 
 	\item S420/620 Introduction to Mathematical Statistics (Spring 2013, B. Luen)
 	\item S432/632 Applied Linear Models II (Spring 2013, C. Huang)
 	\item S431/631 Applied Linear Models I (Fall 2012, C. Huang)
 	\item S426/626 Bayesian Theory and Data Analysis (Fall 2012, G. Huerta, now at Univeristy of New Mexico).
 	\item K310 Statistical Techniques (Spring 2012, S. Sang, now at University of Mississippi)
 	\end{itemize}
 \item National Chengchi University \hfill
 	\begin{itemize} \itemsep -2pt 
 	\item Principle of Macroeconomics (Spring 2005)
 	\item Business Statistics (Fall 2004)
 	\item Intermediate Microeconomics (Fall 2003)

 	\end{itemize}
 \end{itemize}
  \vspace{-0.3cm} 
 {\bf \texttt{R} Workshop Assistant,} Indiana Statistical Consulting Center \hfill Fall 2012
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item tutoring on data management, descriptive statistics, graphics, linear regression, testing, creating functions and basic if-else and for loop statement
 \end{itemize} 
 
 {\bf Second Lieutenant,} Kaohsiung, Taiwan \hfill 2005 - 2007
%{\bf 2nd Lieutenant Platoon Leader,} Chung-Cheng Armed Forces Preparatory School, Kaohsiung, Taiwan \hfill Oct 2005 - Jan 2007

\section{Professional Certificates} 

		      {\bf Statistics}     \hfill
		      \begin{itemize} \itemsep -2pt
		      \item Specialist of Applied Statistics (SAS programming on multivariate analysis), Taiwan Applied Statistics Association \hfill 2007
		      \end{itemize}
              {\bf Programming}     \hfill		       
		      \begin{itemize} \itemsep -2pt
		      \item \texttt{C/C++} Training Program, Department of Computer Science and Information Engineering, National Taiwan University \hfill 2008
		      \end{itemize}
		      {\bf Finance}        
	          \begin{itemize} \itemsep -2pt
		      \item Senior Securities Specialist, Taiwan Securities Association  \hfill 2006
		      \item Trust Specialist, Trust Association of Taiwan \hfill 2006
		      \item Securities Investment Trust and Consulting Professionals, Securities Investment and Consulting Association of Taiwan \hfill 2006
		      \item Financial Planning Personnel, Taiwan Academy of Banking and Finance \hfill 2006
		      \item Bank Internal Control and Audit, Taiwan Academy of Banking and Finance \hfill 2006       
		      \end{itemize}	      
%		      {\bf Web management}     \hfill		       
%		      \begin{itemize} \itemsep -2pt
%		      \item Web Site Development Fundamentals, University Information Technology Service, Indiana University Bloomington
%		      \end{itemize}		
%		      \begin{itemize}	            	      
%		      \item Web Markup \& Style Coding, University Information Technology Service, Indiana University Bloomington
%		      \end{itemize}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{MOOC Certificates}
%{\bf Programming}     \hfill
{\bf Coursera}
 \begin{itemize} \itemsep -2pt
 \item Data Science Specialization, Johns Hopkins University (completed all courses except Developing Data Products and Capstone Project)
 \item Python Programming
 \begin{itemize}\itemsep -2pt
 	\item Using Python to Access Web Data, University of Michigan
 	\item An Introduction to Interactive Programming in Python, Rice Univerisity
 	\item Introduction to Python programming, University of Toronto
 \end{itemize}
 \end{itemize}
  \vspace{-0.3cm} 
 {\bf Udemy}
 \begin{itemize}
 	\item Python for Data Analysis and Visualization
 	\item Python for Data Science and Machine Learning
 \end{itemize}
% Exploratory Data Analysis, Johns Hopkins University, \hfill In progress
% \item The Data Scientist's Toolbox, Johns Hopkins University, \hfill 2014
% \item \texttt{R} Programming, Johns Hopkins University, \hfill 2014
% \item Getting and Cleaning Data, Johns Hopkins University, \hfill 2014 
% \item Introduction to Python programming, University of Toronto \hfill 2013


%\section{Languages}
%   %\begin{tabular}{l p{3in}}
%%    \underline{Speaking:}\\
%%    Native: Mandarin\\
%%    Fluent: English\\
%%    Basic: Japanese  
%    
%    \underline{Scientific and Statistical Computing:} \\
%    Fluent: \texttt{R}, \texttt{MATLAB}, \texttt{WinBUGS/OpenBUGS}\\
%    Good: SAS, SPSS, Stata\\
%    Basic: Julia   
%    
%    \underline{General Programming:}\\
%    Good: \texttt{C/C++}, Python\\
%    Basic: Perl
%    \underline{Markup:}\\
%    Fluent: {\LaTeX}\\
%    Good: LyX, Vim, Emacs(ESS), HTML\\
% %\end{tabular}

\section{Programming Languages}
	\underline{Scientific and Statistical Computing:} Fluent: R. Good: MATLAB, SAS, SPSS, Stata, WinBUGS/OpenBUGS.\\
    \underline{General Programming:} Good: Python (NumPy, Scipy, pandas, matplotlib, seaborn). Basic: Fortran, C/C++ (Rcpp package)\\
    \underline{Markup:} Fluent: {\LaTeX}, Markdown. Good: HTML/CSS. \\
    
%\section{Computer skills}
	
%    \underline{Operating Systems:} Windows, Mac OSX, Unix, Ubuntu\\
%    \underline{Graphics:} GGobi\\
%    \underline{Others:} Microsoft Office, Dreamwaever, 
 
\section{Academic Honors}
Runner-up of ASA Statistics in Imaging Section Student Paper Competition for JSM \hfill 2017\\
Chanceller's Fellowship, University of California, Santa Cruz\hfill 2013\\
Graduate Scholarship, Taiwan Student Association, Indiana University \hfill 2009\\
Graduate Scholarship, American International Education Foundation  \hfill 2008\\
Excellence during Military Service, Ministry of National Defense, Taiwan \hfill 2007\\
Honorary Member of the Phi Tau Phi Scholastic Honor Society of Taiwan \hfill 2005\\
Teaching Excellence Award (Microeconomics, Business Statistics) \hfill 2004, 2005\\
Department Graduate Fellowship, National Chengchi University \hfill 2004, 2005\\
Hsing-Hua Liu Scholarship, National Chengchi University \hfill 2002\\
National Chengchi University Presidential Awards \hfill 2001\\
\textit{Awarded to the top 5\% students in each department}


%\section{Activities}
%IT training, Indiana University Bloomington  \hfill 2011-2013\\
%Workshop in Methods, Indiana University Bloomington  \hfill 2011-2013\\
%Midwest Statistics Research Colloquium, University of Wisconsin-Madison  \hfill 2012 \\
%Stochastic Programming Workshop by Stein Wallace, National Taiwan University \hfill 2011\\
%Taiwan Econometrics Conference, Institute of Economics, Academia Sinica  \hfill 2007 \\

%\section{Services}
%Reviewed a conference paper for conference AI \& Statistics 2013

%\section{Blogs I like}
%Statistical Modeling, Causal Inference, and Social Science, R-bloggers, inside-R, Xi'an's og, Simply Statistics, Learning From Data (Tao Shi), Rob J Hyndman Blog, Normal Deviate, dataists, FlowingData, Three-Toed Sloth




\end{resume} 
\end{document} 



